Equalizer Programming Guide

### 2008-08-29 Developer/ProgrammingGuide/paper.tex
Clean up event interface: - Remove ChannelEvent and WindowEvent: no need to pass pointer of window   and channel, since the receiver is the window or channel - Window::processEvent and Channel::processEvent now receive an eq::Event - rename event.pointerEvent and event.keyEvent to event.pointer and   event.key for consistency with other event names. - Update Programming Guide accordingly
Will test WGL version in a minute.

[ ] May break build
[x] Breaks existing applications
[ ] Bugfix
[ ] New Feature
[x] Cleanup
[ ] Optimization
[x] Documentation

\date{
  \vspace{2cm}
  \begin{figure}[ht]
    \hspace{-4.5cm}\includegraphics[width=22cm]{images/teaser.pdf}
  \end{figure}
  \vspace{1cm}
%  \textbf{RELEASE CANDIDATE}\\[\medskipamount]
  Version 1.3.8 for Equalizer 0.5.4+svn\\[\medskipamount]
  \today
}

@@

\clearpage
\thispagestyle{empty}
\tableofcontents
\vfill{\center\begin{tabularx}{\textwidth}{|l|l|X|}
    \hline
    \bf Rev & \bf Date     & \bf Changes \\
    \hline
    1.0     & Oct 28, 2007 & Initial Version for Equalizer 0.4\\
    1.2     & Apr 15, 2008 & Version for Equalizer 0.5\\
    1.3.1   & May 02, 2008 & Add \sref{sStatistics}, improved images based on 1.2 print\\
    1.3.2   & May 05, 2008 & Add network distribution on eqPly model data\\
    1.3.3   & May 10-19, 2008 & add \aref{aFileFormat}\\
    1.3.4   & July 3, 2008 & Update \sref{sStatistics}\\
    1.3.5   & July 7, 2008 & Update after namespace naming cleanup\\
    1.3.6   & July 20, 2008 & Add accum and samples to \aref{aFileFormat}, add \sref{sDrawableConfig}\\
    1.3.7   & Aug 22, 2008 & Update \sref{sEqplyWIndow} with OSWindow changes\\
    1.3.8   & Aug 25, 2008 & Update \sref{sEventHandling} with OSWindow changes\\
    \hline
  \end{tabularx}}
\thispagestyle{empty}
\clearpage

@@

Events are received by an event handler. The event handler finds the
\textsf{eq::OSWindow} associated to the event. It then creates a generic
\textsf{WindowEvent}, which holds the event data in an independent
format. The original native event and this generic \textsf{WindowEvent}
form the \textsf{OSWindowEvent}, which is passed to the concrete
\textsf{OSWindow} for processing.

\begin{wrapfigure}{r}{.382\textwidth}
  \includegraphics[width=.382\textwidth]{images/eventFilter.pdf}
  {\caption{\small\label{fEventProcessing}Event Processing}}
\end{wrapfigure}
The purpose of the \textsf{OSWindow} processing method,
\textsf{processEvent}, is to perform window-system specific event
processing. For example, \textsf{AGLWindow::processEvent} calls
\textsf{aglUpdateContext} whenever a resize event is received. For
further processing, the \textsf{WindowEvent} is passed on to
\textsf{Window::processEvent}. This \textsf{WindowEvent} no longer contains
the native event.

>>>>

\date{
  \vspace{2cm}
  \begin{figure}[ht]
    \hspace{-4.5cm}\includegraphics[width=22cm]{images/teaser.pdf}
  \end{figure}
  \vspace{1cm}
%  \textbf{RELEASE CANDIDATE}\\[\medskipamount]
  Version 1.3.9 for Equalizer 0.5.4+svn\\[\medskipamount]
  \today
}

@@

\clearpage
\thispagestyle{empty}
\tableofcontents
\vfill{\center\begin{tabularx}{\textwidth}{|l|l|X|}
    \hline
    \bf Rev & \bf Date     & \bf Changes \\
    \hline
    1.0     & Oct 28, 2007 & Initial Version for Equalizer 0.4\\
    1.2     & Apr 15, 2008 & Version for Equalizer 0.5\\
    1.3.1   & May 02, 2008 & Add \sref{sStatistics}, improved images based on 1.2 print\\
    1.3.2   & May 05, 2008 & Add network distribution on eqPly model data\\
    1.3.3   & May 10-19, 2008 & add \aref{aFileFormat}\\
    1.3.4   & July 3, 2008 & Update \sref{sStatistics}\\
    1.3.5   & July 7, 2008 & Update after namespace naming cleanup\\
    1.3.6   & July 20, 2008 & Add accum and samples to \aref{aFileFormat}, add \sref{sDrawableConfig}\\
    1.3.7   & Aug 22, 2008 & Update \sref{sEqplyWIndow} with OSWindow changes\\
    1.3.8   & Aug 25, 2008 & Update \sref{sEventHandling} with OSWindow changes\\
    1.3.9   & Aug 29, 2008 & Update \sref{sEventHandling}: event handling cleanup\\
    \hline
  \end{tabularx}}
\thispagestyle{empty}
\clearpage

@@

Events are received by an event handler. The event handler finds the
\textsf{eq::OSWindow} associated to the event. It then creates a generic
\textsf{Event}, which holds the event data in an independent
format. The original native event and this generic \textsf{Event}
form the \textsf{OSWindowEvent}, which is passed to the concrete
\textsf{OSWindow} for processing.

\begin{wrapfigure}{r}{.382\textwidth}
  \includegraphics[width=.382\textwidth]{images/eventFilter.pdf}
  {\caption{\small\label{fEventProcessing}Event Processing}}
\end{wrapfigure}
The purpose of the \textsf{OSWindow} processing method,
\textsf{processEvent}, is to perform window-system specific event
processing. For example, \textsf{AGLWindow::processEvent} calls
\textsf{aglUpdateContext} whenever a resize event is received. For
further processing, the \textsf{Event} is passed on to
\textsf{Window::processEvent}. This \textsf{Event} no longer contains
the native event.
